---
title: "City Say-Do Gap — Core Analysis -- JY 260201"
The final combined figure: SFig3_Desakota_Sensitivity.png
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE,
                      fig.align="center", fig.retina=2, dpi=300)
```

# 0. Setup

```{r packages}
required_pkgs <- c("tidyverse","ppcor","mgcv","AER","patchwork","ggrepel","scales")
for (pkg in required_pkgs) {
  if (!requireNamespace(pkg, quietly=TRUE)) install.packages(pkg)
  library(pkg, character.only=TRUE)
}
```

```{r load-data}
df_raw <- read.csv("data/MergedPanelV5.csv", fileEncoding="latin1", stringsAsFactors=FALSE)
df <- df_raw %>% filter(!city %in% c("Sabah & Sarawak","Davao del Sur","Other"))
cat("Data:", nrow(df), "cities\n")
```

```{r palette}
col_green <- "#4daf4a"; col_orange <- "#ff7f00"; col_blue <- "#377eb8"; col_grey <- "#999999"
country_colors <- c(Indonesia="#e41a1c", Malaysia="#377eb8", Philippines="#984ea3",
                    Singapore="#daa520", Thailand="#00bfc4", Vietnam="#333333")
typology_colors <- c("Green Urban Cores"=col_green, "Grey Urban Cores"=col_grey,
                     "Desakota Belts"=col_orange)
```

# 1. Data Preparation

```{r data-prep}
desa_log_tf <- function(x) { mn <- min(x[x>0], na.rm=TRUE); log(x + mn/2) }

df$Desa_CropOnly_z  <- as.numeric(scale(desa_log_tf(df$Desakota_Index_CropOnly)))
df$Desa_CropGreen_z <- as.numeric(scale(desa_log_tf(df$Desakota_Index_CropAndGreen)))
df$Green_Exposure_z  <- as.numeric(scale(df$Green.Exposure.Index))
df$Blue_Exposure_z   <- as.numeric(scale(df$Blue.Exposure.Index))
df$NC_z       <- as.numeric(scale(df$genGreenConnectness))
df$GDP_per_z  <- as.numeric(scale(df$GDP_per))
df$OnlineExp_z <- as.numeric(scale(df$onlineShoppingExperience))
df$HighEdu_z  <- as.numeric(scale(df$isHighEdu))
df$SocMedia_z <- as.numeric(scale(df$socialMediaHrs))

# Raw gaps (NC models)
df$RG_Grocery_BPN    <- df$stdGreenGroceryLikert_BPN - df$reportMonthlyGreenGrocery_BPN
df$RG_Electronic_BPN <- df$stdGreenElectronicLikert_BPN - df$reportMonthlyGreenElectronic_BPN
df$RB_Grocery_BPN    <- df$reportMonthlyGreenGrocery_BPN - df$greenSpendingShareGrocery_BPN
df$RB_Electronic_BPN <- df$reportMonthlyGreenElectronic_BPN - df$greenSpendingShareElectronic_BPN
df$RG_Grocery_LPM    <- df$stdGreenGroceryLikert_LPM - df$reportMonthlyGreenGrocery_LPM
df$RG_Electronic_LPM <- df$stdGreenElectronicLikert_LPM - df$reportMonthlyGreenElectronic_LPM
df$RB_Grocery_LPM    <- df$reportMonthlyGreenGrocery_LPM - df$greenSpendingShareGrocery_LPM
df$RB_Electronic_LPM <- df$reportMonthlyGreenElectronic_LPM - df$greenSpendingShareElectronic_LPM

# Z-scored DVs (spatial models) — each computed independently
df$Obs_Grocery_LPM_z    <- as.numeric(scale(df$greenSpendingShareGrocery_LPM))
df$Obs_Electronic_LPM_z <- as.numeric(scale(df$greenSpendingShareElectronic_LPM))
df$Obs_Grocery_BPN_z    <- as.numeric(scale(df$greenSpendingShareGrocery_BPN))
df$Obs_Electronic_BPN_z <- as.numeric(scale(df$greenSpendingShareElectronic_BPN))

# Z-scored gap components — scale each raw column first, then subtract
# NOTE: RG = scale(Reported) - scale(Intention)  [positive = over-reporting relative to intention]
# LPM
df$RG_Grocery_LPM_z    <- as.numeric(scale(df$reportMonthlyGreenGrocery_LPM)) -
                            as.numeric(scale(df$stdGreenGroceryLikert_LPM))
df$RG_Electronic_LPM_z <- as.numeric(scale(df$reportMonthlyGreenElectronic_LPM)) -
                            as.numeric(scale(df$stdGreenElectronicLikert_LPM))
df$RB_Grocery_LPM_z    <- as.numeric(scale(df$reportMonthlyGreenGrocery_LPM)) -
                            as.numeric(scale(df$greenSpendingShareGrocery_LPM))
df$RB_Electronic_LPM_z <- as.numeric(scale(df$reportMonthlyGreenElectronic_LPM)) -
                            as.numeric(scale(df$greenSpendingShareElectronic_LPM))

ctrl_str <- "GDP_per_z + OnlineExp_z + HighEdu_z + SocMedia_z"

# Diagnostic: confirm Z-scored gap variables exist and have data
cat("=== Z-scored DV non-NA counts ===\n")
for (v in c("Obs_Grocery_LPM_z","RG_Grocery_LPM_z","RB_Grocery_LPM_z",
            "Obs_Electronic_LPM_z","RG_Electronic_LPM_z","RB_Electronic_LPM_z")) {
  cat(sprintf("  %s: %d non-NA\n", v, sum(!is.na(df[[v]]))))
}
```


# 2. NC Models {.tabset}

```{r nc-models}
nc_configs <- tribble(
  ~gap_type, ~framework, ~domain, ~dv_col,
  "RG","BPN","Grocery","RG_Grocery_BPN","RG","BPN","Electronic","RG_Electronic_BPN",
  "RG","LPM","Grocery","RG_Grocery_LPM","RG","LPM","Electronic","RG_Electronic_LPM",
  "RB","BPN","Grocery","RB_Grocery_BPN","RB","BPN","Electronic","RB_Electronic_BPN",
  "RB","LPM","Grocery","RB_Grocery_LPM","RB","LPM","Electronic","RB_Electronic_LPM")
nc_results <- list()
for (i in seq_len(nrow(nc_configs))) {
  fml <- as.formula(paste0(nc_configs$dv_col[i],
           " ~ genGreenConnectness + GDP_per + onlineShoppingExperience + isHighEdu"))
  nc_results[[i]] <- list(config=nc_configs[i,], model=lm(fml, data=df))
}
```

## Gap 1

```{r nc-gap1, results='asis'}
for (i in 1:4) { cat("\n###",nc_configs$framework[i],nc_configs$domain[i],"\n\n"); print(summary(nc_results[[i]]$model)); cat("\n---\n") }
```

## Gap 2

```{r nc-gap2, results='asis'}
for (i in 5:8) { cat("\n###",nc_configs$framework[i],nc_configs$domain[i],"\n\n"); print(summary(nc_results[[i]]$model)); cat("\n---\n") }
```


# 3. Fig 1a — Slope Graph

> **FIX**: Bold-line averages use per-variable means (not complete-case).

```{r fig1a, fig.width=16, fig.height=5.5, fig.cap="**Fig. 1a**"}
make_slope <- function(data, fw, dom) {
  ic <- if(fw=="BPN") paste0("stdGreen",dom,"Likert_BPN") else paste0("stdGreen",dom,"Likert_LPM")
  rc <- if(fw=="BPN") paste0("reportMonthlyGreen",dom,"_BPN") else paste0("reportMonthlyGreen",dom,"_LPM")
  oc <- if(fw=="BPN") paste0("greenSpendingShare",dom,"_BPN") else paste0("greenSpendingShare",dom,"_LPM")
  d <- data[, c("city","Country",ic,rc,oc)]
  names(d) <- c("city","Country","Intention","Reported","Observed")
  d[complete.cases(d), ] %>%
    pivot_longer(c(Intention,Reported,Observed), names_to="stage", values_to="score") %>%
    mutate(stage=factor(stage, levels=c("Intention","Reported","Observed")),
           panel=paste0(fw,", ",dom))
}
slope_data <- bind_rows(make_slope(df,"BPN","Grocery"), make_slope(df,"BPN","Electronic"),
                         make_slope(df,"LPM","Grocery"), make_slope(df,"LPM","Electronic")) %>%
  mutate(panel=factor(panel, levels=c("BPN, Grocery","BPN, Electronic","LPM, Grocery","LPM, Electronic")))

# Per-variable averages (each stage uses all available data for that variable)
make_avg <- function(data, fw, dom) {
  ic <- if(fw=="BPN") paste0("stdGreen",dom,"Likert_BPN") else paste0("stdGreen",dom,"Likert_LPM")
  rc <- if(fw=="BPN") paste0("reportMonthlyGreen",dom,"_BPN") else paste0("reportMonthlyGreen",dom,"_LPM")
  oc <- if(fw=="BPN") paste0("greenSpendingShare",dom,"_BPN") else paste0("greenSpendingShare",dom,"_LPM")
  data.frame(
    panel = paste0(fw,", ",dom),
    stage = factor(c("Intention","Reported","Observed"), levels=c("Intention","Reported","Observed")),
    score = c(mean(data[[ic]], na.rm=TRUE), mean(data[[rc]], na.rm=TRUE), mean(data[[oc]], na.rm=TRUE)),
    stringsAsFactors = FALSE)
}
slope_avg <- rbind(make_avg(df,"BPN","Grocery"), make_avg(df,"BPN","Electronic"),
                    make_avg(df,"LPM","Grocery"), make_avg(df,"LPM","Electronic"))
slope_avg$panel <- factor(slope_avg$panel, levels=levels(slope_data$panel))

slope_cty <- slope_data %>% group_by(panel,stage,Country) %>% summarise(score=mean(score),.groups="drop")

p_fig1a <- ggplot() +
  geom_line(data=slope_data, aes(x=stage,y=score,group=city), alpha=.15, linewidth=.3, colour="grey70") +
  geom_line(data=slope_cty, aes(x=stage,y=score,group=Country,colour=Country), linewidth=.7, alpha=.8) +
  geom_line(data=slope_avg, aes(x=stage,y=score,group=1), linewidth=1.5, colour="black") +
  geom_point(data=slope_avg, aes(x=stage,y=score), size=4, shape=21, fill="white", colour="black", stroke=1.2) +
  geom_text(data=slope_avg, aes(x=stage,y=score,label=sprintf("%.3f",score)), vjust=-1.5, fontface="bold", size=3.5) +
  facet_wrap(~panel,nrow=1) +
  scale_colour_manual(values=country_colors) +
  scale_y_continuous(labels=scales::percent_format(1), limits=c(0,1)) +
  labs(x=NULL, y="Score", tag="a") +
  theme_minimal(base_size=12) +
  theme(legend.position="right", strip.text=element_text(face="bold",size=12), panel.grid.minor=element_blank())
p_fig1a
ggsave("Fig1a_slope_graph.png", p_fig1a, width=16, height=5.5, dpi=300)
```


# 4. Fig 2 — NC Correlation Forest Plot

```{r fig2, fig.width=10, fig.height=10, fig.cap="**Fig. 2**"}
specs1 <- list(
  list("Psychological","Support Environ.\nProtection Action","genGreenAttitude"),
  list("Psychological","Humans Are\nHarming Environ.","genGreenHumanLikert"),
  list("Intention","Grocery","stdGreenGroceryLikert_LPM"),
  list("Intention","Electronics","stdGreenElectronicLikert_LPM"),
  list("Intention","Delivery","stdGreenDeliveryLikert_LPM"),
  list("Intention","Transport","stdGreenWalkLikert_LPM"),
  list("Reported","Grocery","reportMonthlyGreenGrocery_LPM"),
  list("Reported","Electronics","reportMonthlyGreenElectronic_LPM"),
  list("Reported","Delivery","reportMonthlyGreenDelivery_LPM"),
  list("Reported","Transport","reportMonthlyGreenWalk_LPM"))
rows1 <- do.call(rbind, lapply(specs1, function(s) {
  tt <- cor.test(df$genGreenConnectness, df[[s[[3]]]], use="complete.obs")
  data.frame(category=s[[1]], indicator=s[[2]], r=tt$estimate, p=tt$p.value,
             ci_lo=tt$conf.int[1], ci_hi=tt$conf.int[2], stringsAsFactors=FALSE)
}))
obs_specs <- list(
  list("Spending Share","greenSpendingShareGrocery_LPM","greenSpendingShareElectronic_LPM"),
  list("Item Share","greenItemsShareGrocery_LPM","greenItemsShareElectronic_LPM"),
  list("Per-capita Spend","greenMonthlySpendingGrocery","greenMonthlySpendingElectronic"),
  list("Order Share","greenOrdersShareGrocery_LPM","greenOrdersShareElectronic_LPM"))
rows2 <- do.call(rbind, lapply(obs_specs, function(s) {
  tg <- cor.test(df$genGreenConnectness, df[[s[[2]]]], use="complete.obs")
  te <- cor.test(df$genGreenConnectness, df[[s[[3]]]], use="complete.obs")
  rbind(data.frame(category="Observed: Grocery",indicator=s[[1]],r=tg$estimate,p=tg$p.value,
                   ci_lo=tg$conf.int[1],ci_hi=tg$conf.int[2],stringsAsFactors=FALSE),
        data.frame(category="Observed: Electronics",indicator=s[[1]],r=te$estimate,p=te$p.value,
                   ci_lo=te$conf.int[1],ci_hi=te$conf.int[2],stringsAsFactors=FALSE))
}))
all_corr <- rbind(rows1, rows2) %>%
  mutate(sig=case_when(p<.001~"***",p<.01~"**",p<.05~"*",TRUE~"ns"), row_id=rev(row_number()))

p_fig2 <- ggplot(all_corr, aes(x=r,y=reorder(indicator,row_id),colour=category,shape=category)) +
  geom_vline(xintercept=0,linetype="dashed",colour="grey50") +
  geom_pointrange(aes(xmin=ci_lo,xmax=ci_hi),size=.6,linewidth=.8,position=position_dodge(.6)) +
  geom_text(aes(label=paste0("r = ",sprintf("%.2f",r),"  ",sig)),
            hjust=-.15,size=3,show.legend=FALSE,position=position_dodge(.6)) +
  scale_colour_manual(values=c(Psychological="#ff7f00",Intention="#00bfc4",Reported="#984ea3",
    "Observed: Grocery"="#e75480","Observed: Electronics"="#e75480")) +
  scale_shape_manual(values=c(Psychological=16,Intention=16,Reported=16,
    "Observed: Grocery"=16,"Observed: Electronics"=17)) +
  labs(x="Pearson r",y=NULL,colour=NULL,shape=NULL) +
  theme_minimal(base_size=12)+theme(legend.position="bottom",panel.grid.minor=element_blank())
p_fig2
ggsave("Fig2_NC_correlations.png", p_fig2, width=10, height=10, dpi=300)
```


# 5. Mediation Analysis

```{r mediation-helper}
# --- Core mediation function ---
# Total / Direct: OLS with common complete cases + within-sample Z-score
# Indirect (via NC): partial correlation between NC_z and DV

run_spatial_mediation <- function(data, spatial_raw_col, dv_type, domain,
                                  is_desa = FALSE,
                                  d_joint = NULL) {
  int_col  <- paste0("stdGreen", domain, "Likert_LPM")
  rep_col  <- paste0("reportMonthlyGreen", domain, "_LPM")
  obs_col  <- paste0("greenSpendingShare", domain, "_LPM")
  ctrl_cols <- c("GDP_per", "onlineShoppingExperience", "isHighEdu", "socialMediaHrs")

  # --- Total / Direct: per-model complete cases ---
  needed <- c(int_col, rep_col, obs_col, spatial_raw_col, "genGreenConnectness", ctrl_cols)
  cc  <- complete.cases(data[, needed])
  dc  <- data[cc, ]
  n   <- nrow(dc)
  if (n < 20) stop(paste("Only", n, "complete cases"))

  if (is_desa) {
    mn   <- min(dc[[spatial_raw_col]][dc[[spatial_raw_col]] > 0])
    sp_z <- as.numeric(scale(log(dc[[spatial_raw_col]] + mn / 2)))
  } else {
    sp_z <- as.numeric(scale(dc[[spatial_raw_col]]))
  }
  nc_z  <- as.numeric(scale(dc$genGreenConnectness))
  gdp_z <- as.numeric(scale(dc$GDP_per))
  ose_z <- as.numeric(scale(dc$onlineShoppingExperience))
  edu_z <- as.numeric(scale(dc$isHighEdu))
  soc_z <- as.numeric(scale(dc$socialMediaHrs))

  if (dv_type == "Obs") {
    dv_z <- as.numeric(scale(dc[[obs_col]]))
  } else if (dv_type == "RG") {
    # RG = scale(Reported) - scale(Intention)
    dv_z <- as.numeric(scale(dc[[rep_col]])) - as.numeric(scale(dc[[int_col]]))
  } else {
    dv_z <- as.numeric(scale(dc[[rep_col]])) - as.numeric(scale(dc[[obs_col]]))
  }

  tmp <- data.frame(dv = dv_z, sp = sp_z, nc = nc_z,
                    gdp = gdp_z, ose = ose_z, edu = edu_z, soc = soc_z)

  m_tot <- lm(dv ~ sp + gdp + ose + edu + soc, data = tmp)
  m_out <- lm(dv ~ sp + nc + gdp + ose + edu + soc, data = tmp)
  st <- summary(m_tot); so <- summary(m_out)

  # --- Indirect: partial correlation on joint complete-case sample ---
  dv_joint_col <- if (dv_type == "Obs") paste0("Obs_", domain, "_LPM_z") else
                  if (dv_type == "RG")  paste0("RG_",  domain, "_LPM_z") else
                                         paste0("RB_",  domain, "_LPM_z")

  if (!is.null(d_joint) && dv_joint_col %in% names(d_joint)) {
    pc_data <- d_joint[, c(dv_joint_col, "NC_z", "GDP_per_z", "OnlineExp_z", "HighEdu_z", "SocMedia_z")]
    pc  <- ppcor::pcor(pc_data)
    ind_beta <- pc$estimate["NC_z", dv_joint_col]
    ind_p    <- pc$p.value["NC_z", dv_joint_col]
    # Approximate 95% CI via Fisher Z
    n_joint  <- nrow(d_joint)
    k        <- 4   # number of control variables
    se_z     <- 1 / sqrt(n_joint - k - 3)
    fz       <- atanh(ind_beta)
    ind_ci_lo <- tanh(fz - 1.96 * se_z)
    ind_ci_hi <- tanh(fz + 1.96 * se_z)
  } else {
    ind_beta <- ind_p <- ind_ci_lo <- ind_ci_hi <- NA_real_
  }

  data.frame(
    total_effect   = coef(m_tot)["sp"],
    direct_effect  = coef(m_out)["sp"],
    indirect_effect = ind_beta,
    total_p        = st$coefficients["sp", 4],
    direct_p       = so$coefficients["sp", 4],
    indirect_p     = ind_p,
    total_ci_lo    = confint(m_tot)["sp", 1],
    total_ci_hi    = confint(m_tot)["sp", 2],
    direct_ci_lo   = confint(m_out)["sp", 1],
    direct_ci_hi   = confint(m_out)["sp", 2],
    indirect_ci_lo = ind_ci_lo,
    indirect_ci_hi = ind_ci_hi,
    n = n, r2_total = st$r.squared, r2_direct = so$r.squared,
    stringsAsFactors = FALSE)
}
```

```{r mediation-run}
needed_joint <- c("RG_Grocery_LPM_z", "RG_Electronic_LPM_z",
                  "RB_Grocery_LPM_z", "RB_Electronic_LPM_z",
                  "Obs_Grocery_LPM_z", "Obs_Electronic_LPM_z",
                  "Green_Exposure_z", "Desa_CropOnly_z",
                  "NC_z", "GDP_per_z", "OnlineExp_z", "HighEdu_z", "SocMedia_z")
d_joint <- df[complete.cases(df[, needed_joint]), ]
cat("Joint complete-case N =", nrow(d_joint), "\n")

# ---- Run all spatial × DV combinations ----
sp_cfgs <- expand.grid(
  spatial_raw_col = c("Green.Exposure.Index", "Desakota_Index_CropOnly",
                       "Desakota_Index_CropAndGreen", "Blue.Exposure.Index"),
  domain  = c("Grocery", "Electronic"),
  dv_type = c("RG", "RB", "Obs"),
  stringsAsFactors = FALSE)
sp_cfgs$is_desa <- grepl("Desakota", sp_cfgs$spatial_raw_col)
sp_cfgs$spatial_label <- with(sp_cfgs, case_when(
  spatial_raw_col == "Green.Exposure.Index"        ~ "Green Exposure",
  spatial_raw_col == "Desakota_Index_CropOnly"     ~ "Desakota (Crop Only)",
  spatial_raw_col == "Desakota_Index_CropAndGreen" ~ "Desakota (Crop & Green)",
  spatial_raw_col == "Blue.Exposure.Index"         ~ "Blue Exposure"))

med_list <- list()
for (i in seq_len(nrow(sp_cfgs))) {
  cfg <- sp_cfgs[i, ]
  cat(sprintf("[%d/%d] %s -> %s %s ... ", i, nrow(sp_cfgs),
              cfg$spatial_label, cfg$domain, cfg$dv_type))
  r <- tryCatch(
    run_spatial_mediation(df, cfg$spatial_raw_col, cfg$dv_type,
                          cfg$domain, cfg$is_desa, d_joint),
    error = function(e) { cat("FAIL:", e$message, "\n"); NULL })
  if (!is.null(r)) {
    med_list[[length(med_list) + 1]] <- cbind(cfg, r)
    cat(sprintf("OK N=%d T=%.3f D=%.3f I=%.3f\n",
                r$n, r$total_effect, r$direct_effect, r$indirect_effect))
  }
}
mediation_results <- do.call(rbind, med_list)
rownames(mediation_results) <- NULL
cat(sprintf("\nMediation: %d/%d succeeded\n", nrow(mediation_results), nrow(sp_cfgs)))
print(table(mediation_results$dv_type, mediation_results$spatial_label))
```

# 6. OLS + GAM + Tobit

```{r ols-gam-tobit}
sp_dom <- expand.grid(spatial_var=c("Desa_CropOnly_z","Green_Exposure_z"),
                       domain=c("Grocery","Electronic"), stringsAsFactors=FALSE)
sp_dom$dv_var <- ifelse(sp_dom$domain=="Grocery","Obs_Grocery_LPM_z","Obs_Electronic_LPM_z")

ols_fits <- gam_fits <- tobit_fits <- list()
for (i in seq_len(nrow(sp_dom))) {
  cfg <- sp_dom[i,]
  ols_fits[[i]] <- lm(as.formula(paste(cfg$dv_var,"~",cfg$spatial_var,"+",ctrl_str)), data=df)
  gam_fits[[i]] <- gam(as.formula(paste(cfg$dv_var,"~ s(",cfg$spatial_var,") +",ctrl_str)),
                        data=df, method="REML")
  lc <- min(df[[cfg$dv_var]], na.rm=TRUE)
  tobit_fits[[i]] <- tryCatch(AER::tobit(as.formula(paste(cfg$dv_var,"~",cfg$spatial_var,"+",ctrl_str)),
               data=df, left=lc), error=function(e) NULL)
  cat(sprintf("%s -> %s: OLS b=%.3f R2=%.3f | GAM edf=%.1f R2=%.3f\n",
      cfg$spatial_var, cfg$domain, coef(ols_fits[[i]])[cfg$spatial_var],
      summary(ols_fits[[i]])$r.squared, summary(gam_fits[[i]])$s.table[1,"edf"],
      summary(gam_fits[[i]])$r.sq))
}
```

```{r tobit-table}
for (i in seq_len(nrow(sp_dom))) {
  if (!is.null(tobit_fits[[i]])) {
    cat(sprintf("\n--- Tobit: %s -> %s ---\n", sp_dom$spatial_var[i], sp_dom$dv_var[i]))
    print(summary(tobit_fits[[i]])$coefficients)
  }
}
```


# 7. Fig 4a — Forest Plot (3 columns: RG, RB, Obs)

```{r fig4a, fig.width=14, fig.height=8, fig.cap="**Fig. 4a**"}
fig4a_sub <- mediation_results[mediation_results$spatial_label %in%
               c("Green Exposure", "Desakota (Crop Only)"), ]

cat("Fig4a rows:", nrow(fig4a_sub), "\n")
cat("dv_type distribution:\n"); print(table(fig4a_sub$dv_type, fig4a_sub$spatial_label))

# If RG/RB are missing from mediation, fall back to simple OLS for those
present_types <- unique(fig4a_sub$dv_type)
missing_types <- setdiff(c("RG","RB","Obs"), present_types)

if (length(missing_types) > 0) {
  cat("\n*** Mediation missing for:", paste(missing_types, collapse=", "), "***\n")
  cat("*** Adding OLS-based Total/Direct/Indirect for missing types ***\n")
  
  for (mt in missing_types) {
    for (sv in c("Green_Exposure_z","Desa_CropOnly_z")) {
      for (dom in c("Grocery","Electronic")) {
        dv <- switch(paste0(mt,"_",dom,"_LPM"),
                     RG_Grocery_LPM = "RG_Grocery_LPM_z",
                     RG_Electronic_LPM = "RG_Electronic_LPM_z",
                     RB_Grocery_LPM = "RB_Grocery_LPM_z",
                     RB_Electronic_LPM = "RB_Electronic_LPM_z")
        if (is.null(dv)) next
        
        sl <- ifelse(sv=="Green_Exposure_z","Green Exposure","Desakota (Crop Only)")
        
        # Total: DV ~ Spatial + Controls
        m_tot <- tryCatch(lm(as.formula(paste(dv,"~",sv,"+",ctrl_str)), data=df), error=function(e) NULL)
        # Direct: DV ~ Spatial + NC + Controls
        m_dir <- tryCatch(lm(as.formula(paste(dv,"~",sv,"+ NC_z +",ctrl_str)), data=df), error=function(e) NULL)
        # Mediator: NC ~ Spatial + Controls
        m_med <- tryCatch(lm(as.formula(paste("NC_z ~",sv,"+",ctrl_str)), data=df), error=function(e) NULL)
        
        if (!is.null(m_tot) && !is.null(m_dir) && !is.null(m_med)) {
          total_b <- coef(m_tot)[sv]
          direct_b <- coef(m_dir)[sv]
          indirect_b <- coef(m_med)[sv] * coef(m_dir)["NC_z"]
          st <- summary(m_tot); sd <- summary(m_dir)
          
          fallback <- data.frame(
            spatial_var=sv, domain=dom, dv_type=mt, dv_var=dv, spatial_label=sl,
            total_effect=total_b, direct_effect=direct_b, indirect_effect=indirect_b,
            total_p=st$coefficients[sv,4], direct_p=sd$coefficients[sv,4],
            indirect_p=NA_real_,
            total_ci_lo=confint(m_tot)[sv,1], total_ci_hi=confint(m_tot)[sv,2],
            direct_ci_lo=confint(m_dir)[sv,1], direct_ci_hi=confint(m_dir)[sv,2],
            indirect_ci_lo=NA_real_, indirect_ci_hi=NA_real_,
            n=nobs(m_tot), r2_total=st$r.squared, r2_direct=sd$r.squared,
            stringsAsFactors=FALSE)
          fig4a_sub <- rbind(fig4a_sub, fallback)
        }
      }
    }
  }
}

# Build long format
fig4a_long <- do.call(rbind, lapply(seq_len(nrow(fig4a_sub)), function(i) {
  r <- fig4a_sub[i,]
  data.frame(
    spatial_label=r$spatial_label, domain=r$domain, dv_type=r$dv_type,
    effect_type=c("Total Effects","Direct Effect\n(Indep. of NC)","Indirect Effect\n(via NC)"),
    beta=c(r$total_effect, r$direct_effect, r$indirect_effect),
    ci_lo=c(r$total_ci_lo, r$direct_ci_lo, r$indirect_ci_lo),
    ci_hi=c(r$total_ci_hi, r$direct_ci_hi, r$indirect_ci_hi),
    p_val=c(r$total_p, r$direct_p, r$indirect_p),
    stringsAsFactors=FALSE)
}))

fig4a_long$sig <- with(fig4a_long,
  case_when(is.na(p_val)~"", p_val<.001~"***", p_val<.01~"**", p_val<.05~"*", TRUE~"ns"))
fig4a_long$beta_label <- paste0("\u03b2=",sprintf("%.2f",fig4a_long$beta),fig4a_long$sig)

fig4a_long$effect_type <- factor(fig4a_long$effect_type,
  levels=c("Total Effects","Direct Effect\n(Indep. of NC)","Indirect Effect\n(via NC)"))
fig4a_long$dv_label <- factor(case_when(
  fig4a_long$dv_type=="RG"~"Reported Say-do Gap",
  fig4a_long$dv_type=="RB"~"Reporting Bias (Green Illusion)",
  fig4a_long$dv_type=="Obs"~"Observed Market Behavior"),
  levels=c("Reported Say-do Gap","Reporting Bias (Green Illusion)","Observed Market Behavior"))
fig4a_long$row_label <- factor(
  paste0(fig4a_long$spatial_label,", ",fig4a_long$domain),
  levels=c("Green Exposure, Grocery","Green Exposure, Electronic",
           "Desakota (Crop Only), Grocery","Desakota (Crop Only), Electronic"))

p_fig4a <- ggplot(fig4a_long, aes(x=beta,y=row_label,colour=spatial_label,shape=domain)) +
  geom_vline(xintercept=0,linetype="dashed",colour="grey50") +
  geom_pointrange(aes(xmin=ci_lo,xmax=ci_hi),size=.5,linewidth=.7) +
  geom_text(aes(label=beta_label),vjust=-1,size=2.8,show.legend=FALSE) +
  facet_grid(effect_type ~ dv_label, scales="free_x") +
  scale_colour_manual(values=c("Green Exposure"=col_green,"Desakota (Crop Only)"=col_orange)) +
  scale_shape_manual(values=c(Grocery=16,Electronic=17)) +
  labs(x=expression("Regression Coefficient ("*beta*")"),
       y=NULL,colour="Spatial Index",shape="Domain",tag="a") +
  theme_minimal(base_size=11) +
  theme(strip.text.y=element_text(angle=0,face="bold",size=9),
        strip.text.x=element_text(face="bold"),
        strip.background.y=element_rect(fill="grey92",colour=NA),
        legend.position="bottom", panel.spacing.y=unit(.3,"lines"))
p_fig4a
ggsave("Fig4a_forest_plot.png", p_fig4a, width=14, height=8, dpi=300)
```


# 8. Fig 4b — GAM Scatter (overlaid)

```{r fig4b, fig.width=14, fig.height=6, fig.cap="**Fig. 4b**"}
make_overlay <- function(domain_label) {
  dv <- ifelse(domain_label=="Grocery","Obs_Grocery_LPM_z","Obs_Electronic_LPM_z")
  idx_d <- which(sp_dom$spatial_var=="Desa_CropOnly_z" & sp_dom$domain==domain_label)
  idx_g <- which(sp_dom$spatial_var=="Green_Exposure_z" & sp_dom$domain==domain_label)
  d_all <- df[!is.na(df$Desa_CropOnly_z) & !is.na(df$Green_Exposure_z) & !is.na(df[[dv]]),]

  make_pred <- function(sp,m_ols,m_gam) {
    rng <- range(d_all[[sp]],na.rm=TRUE)
    nd <- data.frame(x=seq(rng[1],rng[2],length.out=200),GDP_per_z=0,OnlineExp_z=0,HighEdu_z=0,SocMedia_z=0)
    names(nd)[1] <- sp
    gp <- predict(m_gam,newdata=nd,se.fit=TRUE)
    nd$gam_fit <- gp$fit; nd$gam_lo <- gp$fit-1.96*gp$se.fit; nd$gam_hi <- gp$fit+1.96*gp$se.fit
    nd$ols_fit <- predict(m_ols,newdata=nd); nd$sp_val <- nd[[sp]]; nd
  }
  pred_d <- make_pred("Desa_CropOnly_z",ols_fits[[idx_d]],gam_fits[[idx_d]])
  pred_g <- make_pred("Green_Exposure_z",ols_fits[[idx_g]],gam_fits[[idx_g]])

  make_lbl <- function(sp_lab,m_ols,m_gam,sp_var) {
    ob <- coef(m_ols)[sp_var]; or2 <- summary(m_ols)$r.squared
    op <- summary(m_ols)$coefficients[sp_var,4]
    osig <- ifelse(op<.001,"***",ifelse(op<.01,"**",ifelse(op<.05,"*","ns")))
    gs <- summary(m_gam); ge <- gs$s.table[1,"edf"]; gr2 <- gs$r.sq
    gp2 <- gs$s.table[1,"p-value"]
    gsig <- ifelse(gp2<.001,"***",ifelse(gp2<.01,"**",ifelse(gp2<.05,"*","ns")))
    paste0(sp_lab,"\nOLS: \u03b2=",sprintf("%.2f",ob),osig,"  R\u00b2=",sprintf("%.3f",or2),
           "\nGAM: edf=",sprintf("%.1f",ge),gsig,"  R\u00b2=",sprintf("%.3f",gr2))
  }
  lbl_d <- make_lbl("Desakota",ols_fits[[idx_d]],gam_fits[[idx_d]],"Desa_CropOnly_z")
  lbl_g <- make_lbl("Green Exposure",ols_fits[[idx_g]],gam_fits[[idx_g]],"Green_Exposure_z")
  yrng <- range(d_all[[dv]],na.rm=TRUE)

  ggplot() +
    geom_point(data=d_all,aes(x=Desa_CropOnly_z,y=.data[[dv]]),colour=col_orange,alpha=.4,size=1.5)+
    geom_line(data=pred_d,aes(x=sp_val,y=ols_fit),linetype="dashed",colour=col_orange,linewidth=.7)+
    geom_ribbon(data=pred_d,aes(x=sp_val,ymin=gam_lo,ymax=gam_hi),fill=col_orange,alpha=.15)+
    geom_line(data=pred_d,aes(x=sp_val,y=gam_fit),colour=col_orange,linewidth=1.2)+
    geom_point(data=d_all,aes(x=Green_Exposure_z,y=.data[[dv]]),colour=col_green,alpha=.4,size=1.5,shape=17)+
    geom_line(data=pred_g,aes(x=sp_val,y=ols_fit),linetype="dashed",colour=col_green,linewidth=.7)+
    geom_ribbon(data=pred_g,aes(x=sp_val,ymin=gam_lo,ymax=gam_hi),fill=col_green,alpha=.15)+
    geom_line(data=pred_g,aes(x=sp_val,y=gam_fit),colour=col_green,linewidth=1.2)+
    annotate("label",x=-2.8,y=yrng[2]-.1,label=lbl_d,hjust=0,vjust=1,size=3,fill="white",colour=col_orange,label.size=.5)+
    annotate("label",x=-2.8,y=yrng[1]+.8,label=lbl_g,hjust=0,vjust=1,size=3,fill="white",colour=col_green,label.size=.5)+
    labs(x="Spatial Index (Z-Score)",y="Observed Market Behavior (Z-Score)",title=domain_label)+
    theme_minimal(base_size=11)+theme(plot.title=element_text(face="bold",hjust=.5))
}
p_fig4b <- make_overlay("Grocery") | make_overlay("Electronic")
p_fig4b
ggsave("Fig4b_GAM_scatter.png", p_fig4b, width=14, height=6, dpi=300)
```


# 9. Fig 5 — City Classification {.tabset}

```{r city-class}
df$urban_typology <- NA_character_
ok <- !is.na(df$Desa_CropOnly_z) & !is.na(df$Green_Exposure_z)
df$urban_typology[ok & df$Desa_CropOnly_z >= 0] <- "Desakota Belts"
df$urban_typology[ok & df$Desa_CropOnly_z < 0 & df$Green_Exposure_z >= 0] <- "Green Urban Cores"
df$urban_typology[ok & df$Desa_CropOnly_z < 0 & df$Green_Exposure_z < 0]  <- "Grey Urban Cores"
cat("Classification:\n"); print(table(df$urban_typology, useNA="always"))
```

## a. Scatter

```{r fig5a, fig.width=10, fig.height=8, fig.cap="**Fig. 5a**"}
df_plot <- df[!is.na(df$urban_typology),]
df_labels <- df_plot[df_plot$isCapitalCity==1 | df_plot$city %in%
  c("Jakarta","Singapore","Bangkok_Metropolis","Metro_Manila","Kuala_Lumpur","Hanoi","HCMC"),]

p_fig5a <- ggplot(df_plot, aes(x=Desa_CropOnly_z,y=Green_Exposure_z,colour=Country))+
  annotate("rect",xmin=-Inf,xmax=0,ymin=0,ymax=Inf,fill=col_green,alpha=.08)+
  annotate("rect",xmin=-Inf,xmax=0,ymin=-Inf,ymax=0,fill="grey80",alpha=.15)+
  annotate("rect",xmin=0,xmax=Inf,ymin=-Inf,ymax=Inf,fill=col_orange,alpha=.08)+
  geom_hline(yintercept=0,linetype="dashed",colour="grey50")+
  geom_vline(xintercept=0,linetype="dashed",colour="grey50")+
  geom_point(size=2.5,alpha=.8)+
  geom_text_repel(data=df_labels, aes(label=city), colour="black", size=3, max.overlaps=20, fontface="italic")+
  scale_colour_manual(values=country_colors)+
  annotate("text",x=-3.2,y=2.4,label="Green Urban Cores",colour=col_green,fontface="bold",hjust=0,size=4)+
  annotate("text",x=-3.2,y=-2.8,label="Grey Urban Cores",colour="grey50",fontface="bold",hjust=0,size=4)+
  annotate("text",x=0.8,y=-2.8,label="Desakota Belts",colour=col_orange,fontface="bold",hjust=0,size=4)+
  labs(x="Desakota Index: Crop Only (Z-Score)",y="Green Exposure Index (Z-Score)",
       title="Morphological Classification",tag="a")+
  theme_minimal(base_size=12)+theme(legend.position="bottom")
p_fig5a
ggsave("Fig5a_scatter.png", p_fig5a, width=10, height=8, dpi=300)
```

## b. Profiles

```{r fig5b, fig.width=8, fig.height=5, fig.cap="**Fig. 5b**"}
# Build manually — no pipes
typs <- c("Green Urban Cores","Grey Urban Cores","Desakota Belts")
mets <- c("Reported Gap","Reporting Bias","Observed Market Behavior")
dvs  <- c("RG_Grocery_LPM_z","RB_Grocery_LPM_z","Obs_Grocery_LPM_z")
prof <- expand.grid(urban_typology=typs, metric=mets, stringsAsFactors=FALSE)
prof$val <- NA_real_
for (j in seq_along(typs)) {
  sub <- df[!is.na(df$urban_typology) & df$urban_typology==typs[j], ]
  for (k in seq_along(mets)) {
    prof$val[prof$urban_typology==typs[j] & prof$metric==mets[k]] <- mean(sub[[dvs[k]]], na.rm=TRUE)
  }
}
prof$metric <- factor(prof$metric, levels=mets)

p_fig5b <- ggplot(prof, aes(x=metric, y=val, fill=urban_typology))+
  geom_col(position=position_dodge(.7), width=.6)+
  geom_hline(yintercept=0,linetype="dashed",colour="grey50")+
  scale_fill_manual(values=typology_colors)+
  labs(x=NULL,y="Average Z-Score",title="Behavioral Profiles by Zone",fill="Urban Typology",tag="b")+
  theme_minimal(base_size=11)+theme(legend.position="bottom")
p_fig5b
ggsave("Fig5b_profiles.png", p_fig5b, width=8, height=5, dpi=300)
```

## c. City Composition by Country

> **FIX**: label positions computed manually — avoids `position_stack + geom_text` gg_par bug.

```{r fig5c, fig.width=10, fig.height=5, fig.cap="**Fig. 5c**"}
# Build composition data manually
comp_raw <- as.data.frame(table(
  Country = df$Country[!is.na(df$urban_typology)],
  urban_typology = df$urban_typology[!is.na(df$urban_typology)]),
  stringsAsFactors = FALSE)
names(comp_raw)[3] <- "n"
comp_raw <- comp_raw[comp_raw$n > 0, ]

# Compute proportions and label positions MANUALLY
comp_list <- list()
for (cty in unique(comp_raw$Country)) {
  sub <- comp_raw[comp_raw$Country == cty, ]
  sub <- sub[order(sub$urban_typology), ]  # consistent order
  sub$pct <- sub$n / sum(sub$n)
  sub$cum_pct <- cumsum(sub$pct)
  sub$label_y <- sub$cum_pct - sub$pct / 2  # center of each bar segment
  sub$label <- paste0(sub$n, " (", round(sub$pct * 100), "%)")
  comp_list[[cty]] <- sub
}
comp_data <- do.call(rbind, comp_list)
rownames(comp_data) <- NULL

p_fig5c <- ggplot(comp_data, aes(x = Country, y = pct, fill = urban_typology)) +
  geom_col(width = .7, colour = "white", linewidth = .3) +
  geom_text(aes(y = label_y, label = label), size = 2.8) +
  scale_fill_manual(values = typology_colors) +
  scale_y_continuous(labels = scales::percent_format(1)) +
  labs(x = NULL, y = "Proportion", fill = "Urban Typology",
       title = "City Composition by Country", tag = "c") +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 30, hjust = 1))
p_fig5c
ggsave("Fig5c_composition.png", p_fig5c, width = 10, height = 5, dpi = 300)
```



# 10. Save Core Results

```{r save-core}
save(df, nc_results, mediation_results, ols_fits, gam_fits, tobit_fits,
     file = "analysis_core_results.RData")
cat("Saved analysis_core_results.RData\n")
```


# 11. Robustness Helper: Unified Sensitivity Engine

> All sensitivity analyses use the SAME specification as the main analysis

```{r sensitivity-engine}
# Significance stars helper (also used by Sections 12-14)
get_stars <- function(p) {
  ifelse(is.na(p), "", ifelse(p < .001, "***", ifelse(p < .01, "**", ifelse(p < .05, "*", "ns"))))
}

# DV configurations (6 combos) used by window / weight / CropGreen loops
dv_configs <- list(
  list(dv_type = "Obs", domain = "Grocery"),
  list(dv_type = "Obs", domain = "Electronic"),
  list(dv_type = "RG",  domain = "Grocery"),
  list(dv_type = "RG",  domain = "Electronic"),
  list(dv_type = "RB",  domain = "Grocery"),
  list(dv_type = "RB",  domain = "Electronic")
)

run_sensitivity_model <- function(df_main, desa_named_vec, dv_type, domain) {
  int_col  <- paste0("stdGreen", domain, "Likert_LPM")
  rep_col  <- paste0("reportMonthlyGreen", domain, "_LPM")
  obs_col  <- paste0("greenSpendingShare", domain, "_LPM")
  ctrl_cols <- c("GDP_per", "onlineShoppingExperience", "isHighEdu", "socialMediaHrs")

  d <- df_main
  d$desa_raw <- desa_named_vec[match(d$city, names(desa_named_vec))]

  # Common complete cases (same logic as main analysis)
  needed <- c(int_col, rep_col, obs_col, "desa_raw", "genGreenConnectness", ctrl_cols)
  cc <- complete.cases(d[, needed])
  dc <- d[cc, ]
  n  <- nrow(dc)
  if (n < 20) stop(paste("Only", n, "complete cases"))

  # Z-score WITHIN this complete sample
  mn_desa <- min(dc$desa_raw[dc$desa_raw > 0], na.rm = TRUE)
  sp_z  <- as.numeric(scale(log(dc$desa_raw + mn_desa / 2)))
  nc_z  <- as.numeric(scale(dc$genGreenConnectness))
  gdp_z <- as.numeric(scale(dc$GDP_per))
  ose_z <- as.numeric(scale(dc$onlineShoppingExperience))
  edu_z <- as.numeric(scale(dc$isHighEdu))
  soc_z <- as.numeric(scale(dc$socialMediaHrs))

  # DV: RG = scale(Reported) - scale(Intention) [positive = over-reporting]
  if (dv_type == "Obs") {
    dv_z <- as.numeric(scale(dc[[obs_col]]))
  } else if (dv_type == "RG") {
    dv_z <- as.numeric(scale(dc[[rep_col]])) - as.numeric(scale(dc[[int_col]]))
  } else {
    # RB = scale(Reported) - scale(Observed)
    dv_z <- as.numeric(scale(dc[[rep_col]])) - as.numeric(scale(dc[[obs_col]]))
  }

  tmp <- data.frame(dv = dv_z, sp = sp_z, nc = nc_z,
                    gdp = gdp_z, ose = ose_z, edu = edu_z, soc = soc_z)

  # Total: DV ~ Spatial + Controls
  m_tot <- lm(dv ~ sp + gdp + ose + edu + soc, data = tmp)
  st    <- summary(m_tot)

  # Direct: DV ~ Spatial + NC + Controls
  m_out <- lm(dv ~ sp + nc + gdp + ose + edu + soc, data = tmp)
  so    <- summary(m_out)

  # Indirect (via NC): partial correlation between nc and dv,
  # controlling for gdp + ose + edu + soc — consistent with main Fig 4a method
  pc_data  <- tmp[, c("dv", "nc", "gdp", "ose", "edu", "soc")]
  pc       <- ppcor::pcor(pc_data)
  ind_beta <- pc$estimate["nc", "dv"]
  ind_p    <- pc$p.value["nc", "dv"]
  # 95% CI via Fisher Z transformation (k = 4 controls)
  k        <- 4
  se_z     <- 1 / sqrt(n - k - 3)
  fz       <- atanh(ind_beta)
  ind_ci_lo <- tanh(fz - 1.96 * se_z)
  ind_ci_hi <- tanh(fz + 1.96 * se_z)

  # GAM
  m_gam   <- tryCatch(gam(dv ~ s(sp) + gdp + ose + edu + soc, data = tmp, method = "REML"),
                       error = function(e) NULL)
  gam_edf <- if (!is.null(m_gam)) summary(m_gam)$s.table[1, "edf"] else NA
  gam_r2  <- if (!is.null(m_gam)) summary(m_gam)$r.sq else NA

  data.frame(
    tot_beta  = st$coefficients["sp", "Estimate"],
    tot_ci_lo = confint(m_tot)["sp", 1],
    tot_ci_hi = confint(m_tot)["sp", 2],
    tot_p     = st$coefficients["sp", "Pr(>|t|)"],
    dir_beta  = so$coefficients["sp", "Estimate"],
    dir_ci_lo = confint(m_out)["sp", 1],
    dir_ci_hi = confint(m_out)["sp", 2],
    dir_p     = so$coefficients["sp", "Pr(>|t|)"],
    ind_beta  = ind_beta,
    ind_ci_lo = ind_ci_lo,
    ind_ci_hi = ind_ci_hi,
    ind_p     = ind_p,
    gam_edf   = gam_edf,
    gam_r2    = gam_r2,
    ols_r2    = st$r.squared,
    n         = n,
    stringsAsFactors = FALSE)
}
```


# 12. Robustness: Window Size Sensitivity {.tabset}

> Desakota index recomputed at 8 moving-window sizes (7×7 to 21×21). Baseline = 9×9.

```{r window-run}
desa_win_raw <- read.csv("data/supplementary/STable3_Desakota_window_sensitivity.csv",
                          stringsAsFactors = FALSE, fileEncoding = "UTF-8")
desa_win_raw$city <- gsub(" ", "_", desa_win_raw$city)

windows <- sort(unique(desa_win_raw$window))
baseline_window <- 9

cat("Window sensitivity:", length(unique(desa_win_raw$city)), "cities,",
    length(windows), "windows:", paste(windows, collapse = ", "), "\n")

# Verify city matching
n_matched <- sum(unique(desa_win_raw$city) %in% df$city)
cat("City match rate:", n_matched, "/", length(unique(desa_win_raw$city)), "\n")

win_results <- list()
for (w in windows) {
  desa_sub <- desa_win_raw[desa_win_raw$window == w, ]
  desa_vec <- setNames(desa_sub$Desakota_index, desa_sub$city)
  
  for (dv_cfg in dv_configs) {
    cat(sprintf("  Win %d × %s %s ... ", w, dv_cfg$dv_type, dv_cfg$domain))
    r <- tryCatch(
      run_sensitivity_model(df, desa_vec, dv_cfg$dv_type, dv_cfg$domain),
      error = function(e) { cat("FAIL:", e$message, "\n"); NULL }
    )
    if (!is.null(r)) {
      win_results[[length(win_results) + 1]] <- cbind(
        data.frame(window = w, dv_type = dv_cfg$dv_type, domain = dv_cfg$domain,
                   stringsAsFactors = FALSE), r)
      cat(sprintf("N=%d T=%.3f D=%.3f I=%.3f\n", r$n, r$tot_beta, r$dir_beta, r$ind_beta))
    }
  }
}
win_sens <- do.call(rbind, win_results)
rownames(win_sens) <- NULL

win_sens$tot_sig <- get_stars(win_sens$tot_p)
win_sens$dir_sig <- get_stars(win_sens$dir_p)
win_sens$ind_sig <- get_stars(win_sens$ind_p)
win_sens$is_baseline <- (win_sens$window == baseline_window)

cat(sprintf("\nWindow sensitivity: %d models completed\n", nrow(win_sens)))
```

## Window Results Table

```{r window-table}
knitr::kable(
  win_sens[, c("window", "dv_type", "domain", "tot_beta", "tot_sig",
               "dir_beta", "dir_sig", "ind_beta", "ind_sig", "gam_edf", "n")],
  digits = 3, caption = "Window Size Sensitivity (7×7 to 21×21)")
```

## Fig S-Window: Coefficient Trajectory

```{r fig-window, fig.width=14, fig.height=8, fig.cap="**Supplementary Fig.** | Window size robustness."}
# Reshape to long
win_long <- do.call(rbind, lapply(seq_len(nrow(win_sens)), function(i) {
  r <- win_sens[i, ]
  data.frame(
    window = rep(r$window, 3), dv_type = rep(r$dv_type, 3), domain = rep(r$domain, 3),
    effect = c("Total", "Direct", "Indirect"),
    beta   = c(r$tot_beta, r$dir_beta, r$ind_beta),
    ci_lo  = c(r$tot_ci_lo, r$dir_ci_lo, r$ind_ci_lo),
    ci_hi  = c(r$tot_ci_hi, r$dir_ci_hi, r$ind_ci_hi),
    sig    = c(r$tot_sig, r$dir_sig, r$ind_sig),
    stringsAsFactors = FALSE)
}))

win_long$effect <- factor(win_long$effect, levels = c("Total", "Direct", "Indirect"))
win_long$dv_label <- factor(
  ifelse(win_long$dv_type == "RG", "Reported Say-do Gap",
  ifelse(win_long$dv_type == "RB", "Reporting Bias", "Observed Market Behavior")),
  levels = c("Reported Say-do Gap", "Reporting Bias", "Observed Market Behavior"))

p_win <- ggplot(win_long, aes(x = window, y = beta, colour = effect, shape = effect)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey50") +
  geom_vline(xintercept = baseline_window, linetype = "dotted", colour = "red", linewidth = .5) +
  geom_ribbon(aes(ymin = ci_lo, ymax = ci_hi, fill = effect), alpha = .12, colour = NA) +
  geom_line(linewidth = .8) +
  geom_point(size = 2) +
  facet_grid(domain ~ dv_label, scales = "free_y") +
  scale_colour_manual(values = c(Total = "grey30", Direct = col_orange, Indirect = col_green)) +
  scale_fill_manual(values = c(Total = "grey30", Direct = col_orange, Indirect = col_green)) +
  scale_shape_manual(values = c(Total = 16, Direct = 17, Indirect = 15)) +
  scale_x_continuous(breaks = windows,
                     labels = paste0(windows, "\u00d7", windows)) +
  labs(x = "Moving Window Size", y = expression("Standardised " * beta),
       colour = "Effect", shape = "Effect", fill = "Effect",
       title = "Desakota Index Robustness: Moving Window Size") +
  theme_minimal(base_size = 11) +
  theme(strip.text = element_text(face = "bold"),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1))

p_win
ggsave("FigS_window_sensitivity.png", p_win, width = 14, height = 8, dpi = 300)
```


# 13. Robustness: Weight Sensitivity {.tabset}

> Desakota index recomputed with 3 DesaMix:DesaFrag weight combinations:
> 0.3:0.7, 0.5:0.5 (baseline), 0.7:0.3.

```{r weight-run}
desa_wt_raw <- read.csv("data/supplementary/STable4_Desakota_weight_sensitivity.csv",
                          stringsAsFactors = FALSE, fileEncoding = "UTF-8")
desa_wt_raw$city <- gsub(" ", "_", desa_wt_raw$city)

weight_cases <- sort(unique(desa_wt_raw$weight_case))
baseline_weight <- "0.5_0.5"

cat("Weight sensitivity:", length(unique(desa_wt_raw$city)), "cities,",
    length(weight_cases), "weights:", paste(weight_cases, collapse = ", "), "\n")

n_matched_w <- sum(unique(desa_wt_raw$city) %in% df$city)
cat("City match rate:", n_matched_w, "/", length(unique(desa_wt_raw$city)), "\n")

wt_results <- list()
for (wc in weight_cases) {
  desa_sub <- desa_wt_raw[desa_wt_raw$weight_case == wc, ]
  desa_vec <- setNames(desa_sub$Desakota_index, desa_sub$city)
  
  for (dv_cfg in dv_configs) {
    cat(sprintf("  Wt %s × %s %s ... ", wc, dv_cfg$dv_type, dv_cfg$domain))
    r <- tryCatch(
      run_sensitivity_model(df, desa_vec, dv_cfg$dv_type, dv_cfg$domain),
      error = function(e) { cat("FAIL:", e$message, "\n"); NULL }
    )
    if (!is.null(r)) {
      wt_results[[length(wt_results) + 1]] <- cbind(
        data.frame(weight_case = wc, dv_type = dv_cfg$dv_type, domain = dv_cfg$domain,
                   stringsAsFactors = FALSE), r)
      cat(sprintf("N=%d T=%.3f D=%.3f I=%.3f\n", r$n, r$tot_beta, r$dir_beta, r$ind_beta))
    }
  }
}
wt_sens <- do.call(rbind, wt_results)
rownames(wt_sens) <- NULL

wt_sens$tot_sig <- get_stars(wt_sens$tot_p)
wt_sens$dir_sig <- get_stars(wt_sens$dir_p)
wt_sens$ind_sig <- get_stars(wt_sens$ind_p)
wt_sens$is_baseline <- (wt_sens$weight_case == baseline_weight)

# Pretty labels
wt_sens$weight_label <- ifelse(wt_sens$weight_case == "0.3_0.7", "Mix 0.3 : Frag 0.7",
                        ifelse(wt_sens$weight_case == "0.5_0.5", "Mix 0.5 : Frag 0.5 (baseline)",
                               "Mix 0.7 : Frag 0.3"))

cat(sprintf("\nWeight sensitivity: %d models completed\n", nrow(wt_sens)))
```

## Weight Results Table

```{r weight-table}
knitr::kable(
  wt_sens[, c("weight_case", "dv_type", "domain", "tot_beta", "tot_sig",
              "dir_beta", "dir_sig", "ind_beta", "ind_sig", "gam_edf", "n")],
  digits = 3, caption = "Weight Sensitivity (Mix:Frag = 0.3:0.7, 0.5:0.5, 0.7:0.3)")
```

## Fig S-Weight: Forest Plot Comparison

```{r fig-weight, fig.width=14, fig.height=7, fig.cap="**Supplementary Fig.** | Weight robustness."}
wt_long <- do.call(rbind, lapply(seq_len(nrow(wt_sens)), function(i) {
  r <- wt_sens[i, ]
  data.frame(
    weight_label = rep(r$weight_label, 3), dv_type = rep(r$dv_type, 3), domain = rep(r$domain, 3),
    effect = c("Total", "Direct", "Indirect"),
    beta   = c(r$tot_beta, r$dir_beta, r$ind_beta),
    ci_lo  = c(r$tot_ci_lo, r$dir_ci_lo, r$ind_ci_lo),
    ci_hi  = c(r$tot_ci_hi, r$dir_ci_hi, r$ind_ci_hi),
    sig    = c(r$tot_sig, r$dir_sig, r$ind_sig),
    stringsAsFactors = FALSE)
}))

wt_long$effect <- factor(wt_long$effect, levels = c("Total", "Direct", "Indirect"))
wt_long$dv_label <- factor(
  ifelse(wt_long$dv_type == "RG", "Reported Say-do Gap",
  ifelse(wt_long$dv_type == "RB", "Reporting Bias", "Observed Market Behavior")),
  levels = c("Reported Say-do Gap", "Reporting Bias", "Observed Market Behavior"))
wt_long$weight_label <- factor(wt_long$weight_label, levels = c(
  "Mix 0.3 : Frag 0.7", "Mix 0.5 : Frag 0.5 (baseline)", "Mix 0.7 : Frag 0.3"))
wt_long$beta_label <- paste0(sprintf("%.3f", wt_long$beta), " ", wt_long$sig)

p_wt <- ggplot(wt_long, aes(x = beta, y = weight_label, colour = effect, shape = effect)) +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey50") +
  geom_pointrange(aes(xmin = ci_lo, xmax = ci_hi),
                  size = .4, linewidth = .6,
                  position = position_dodge(width = .5)) +
  geom_text(aes(label = beta_label), vjust = -0.8, size = 2.5,
            show.legend = FALSE, position = position_dodge(width = .5)) +
  facet_grid(domain ~ dv_label, scales = "free_x") +
  scale_colour_manual(values = c(Total = "grey30", Direct = col_orange, Indirect = col_green)) +
  scale_shape_manual(values = c(Total = 16, Direct = 17, Indirect = 15)) +
  labs(x = expression("Standardised " * beta),
       y = NULL, colour = "Effect", shape = "Effect",
       title = "Desakota Index Robustness: Component Weighting") +
  theme_minimal(base_size = 11) +
  theme(strip.text = element_text(face = "bold"), legend.position = "bottom")

p_wt
ggsave("FigS_weight_sensitivity.png", p_wt, width = 14, height = 7, dpi = 300)
```


# 14. Robustness: CropAndGreen Variant {.tabset}

> Main analysis uses Desakota_Index_CropOnly. Here we replicate using
> Desakota_Index_CropAndGreen as a definitional robustness check.

```{r cropgreen-run}
desa_cag_vec <- setNames(df$Desakota_Index_CropAndGreen, df$city)

cag_results <- list()
for (dv_cfg in dv_configs) {
  cat(sprintf("  CropAndGreen × %s %s ... ", dv_cfg$dv_type, dv_cfg$domain))
  r <- tryCatch(
    run_sensitivity_model(df, desa_cag_vec, dv_cfg$dv_type, dv_cfg$domain),
    error = function(e) { cat("FAIL:", e$message, "\n"); NULL }
  )
  if (!is.null(r)) {
    cag_results[[length(cag_results) + 1]] <- cbind(
      data.frame(variant = "CropAndGreen", dv_type = dv_cfg$dv_type,
                 domain = dv_cfg$domain, stringsAsFactors = FALSE), r)
    cat(sprintf("N=%d T=%.3f D=%.3f I=%.3f\n", r$n, r$tot_beta, r$dir_beta, r$ind_beta))
  }
}

desa_co_vec <- setNames(df$Desakota_Index_CropOnly, df$city)
for (dv_cfg in dv_configs) {
  r <- tryCatch(
    run_sensitivity_model(df, desa_co_vec, dv_cfg$dv_type, dv_cfg$domain),
    error = function(e) NULL)
  if (!is.null(r)) {
    cag_results[[length(cag_results) + 1]] <- cbind(
      data.frame(variant = "CropOnly (baseline)", dv_type = dv_cfg$dv_type,
                 domain = dv_cfg$domain, stringsAsFactors = FALSE), r)
  }
}

cag_sens <- do.call(rbind, cag_results)
rownames(cag_sens) <- NULL
cag_sens$tot_sig <- get_stars(cag_sens$tot_p)
cag_sens$dir_sig <- get_stars(cag_sens$dir_p)
cag_sens$ind_sig <- get_stars(cag_sens$ind_p)
```

## CropAndGreen Results Table

```{r cropgreen-table}
knitr::kable(
  cag_sens[, c("variant", "dv_type", "domain", "tot_beta", "tot_sig",
               "dir_beta", "dir_sig", "ind_beta", "ind_sig", "n")],
  digits = 3, caption = "Desakota Definition Sensitivity: CropOnly vs CropAndGreen")
```

## Fig S-CropGreen: Forest Plot

```{r fig-cropgreen, fig.width=14, fig.height=6, fig.cap="**Supplementary Fig.** | Desakota definition robustness."}
cag_long <- do.call(rbind, lapply(seq_len(nrow(cag_sens)), function(i) {
  r <- cag_sens[i, ]
  data.frame(
    variant = rep(r$variant, 3), dv_type = rep(r$dv_type, 3), domain = rep(r$domain, 3),
    effect = c("Total", "Direct", "Indirect"),
    beta   = c(r$tot_beta, r$dir_beta, r$ind_beta),
    ci_lo  = c(r$tot_ci_lo, r$dir_ci_lo, r$ind_ci_lo),
    ci_hi  = c(r$tot_ci_hi, r$dir_ci_hi, r$ind_ci_hi),
    sig    = c(r$tot_sig, r$dir_sig, r$ind_sig),
    stringsAsFactors = FALSE)
}))
cag_long$effect <- factor(cag_long$effect, levels = c("Total", "Direct", "Indirect"))
cag_long$dv_label <- factor(
  ifelse(cag_long$dv_type == "RG", "Reported Say-do Gap",
  ifelse(cag_long$dv_type == "RB", "Reporting Bias", "Observed Market Behavior")),
  levels = c("Reported Say-do Gap", "Reporting Bias", "Observed Market Behavior"))
cag_long$beta_label <- paste0(sprintf("%.3f", cag_long$beta), " ", cag_long$sig)

p_cag <- ggplot(cag_long, aes(x = beta, y = variant, colour = effect, shape = effect)) +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey50") +
  geom_pointrange(aes(xmin = ci_lo, xmax = ci_hi),
                  size = .4, linewidth = .6,
                  position = position_dodge(width = .5)) +
  geom_text(aes(label = beta_label), vjust = -0.8, size = 2.5,
            show.legend = FALSE, position = position_dodge(width = .5)) +
  facet_grid(domain ~ dv_label, scales = "free_x") +
  scale_colour_manual(values = c(Total = "grey30", Direct = col_orange, Indirect = col_green)) +
  scale_shape_manual(values = c(Total = 16, Direct = 17, Indirect = 15)) +
  labs(x = expression("Standardised " * beta),
       y = NULL, colour = "Effect", shape = "Effect",
       title = "Desakota Index Robustness: Crop Definition") +
  theme_minimal(base_size = 11) +
  theme(strip.text = element_text(face = "bold"), legend.position = "bottom")

p_cag
ggsave("FigS_cropgreen_sensitivity.png", p_cag, width = 14, height = 6, dpi = 300)
```


# 15. Save All Results

```{r save-all}
save(df, nc_results, mediation_results, ols_fits, gam_fits, tobit_fits,
     win_sens, wt_sens, cag_sens,
     file = "analysis_all_results.RData")

cat("\n=== All output files ===\n")
cat(paste(list.files(pattern = "\\.(png|RData)$"), collapse = "\n"), "\n")
```


```{r fig-robustness-grocery, fig.width=14, fig.height=12, fig.cap="**Supplementary Fig. S** | Robustness of Desakota Index (Grocery domain)."}

# --- Combine all three sensitivity tables into one long-format data frame ---

# 1. Window
win_part <- do.call(rbind, lapply(seq_len(nrow(win_sens)), function(i) {
  r <- win_sens[i, ]
  data.frame(
    dimension = "Window Size",
    param_value = paste0(r$window, "\u00d7", r$window),
    is_baseline = (r$window == 9),
    dv_type = r$dv_type, domain = r$domain,
    effect = c("Total", "Direct", "Indirect"),
    beta   = c(r$tot_beta, r$dir_beta, r$ind_beta),
    ci_lo  = c(r$tot_ci_lo, r$dir_ci_lo, r$ind_ci_lo),
    ci_hi  = c(r$tot_ci_hi, r$dir_ci_hi, r$ind_ci_hi),
    sig    = c(r$tot_sig, r$dir_sig, r$ind_sig),
    stringsAsFactors = FALSE)
}))

# 2. Weight
wt_part <- do.call(rbind, lapply(seq_len(nrow(wt_sens)), function(i) {
  r <- wt_sens[i, ]
  label <- switch(r$weight_case,
    "0.3_0.7" = "Mix 0.3 : Frag 0.7",
    "0.5_0.5" = "Mix 0.5 : Frag 0.5",
    "0.7_0.3" = "Mix 0.7 : Frag 0.3")
  data.frame(
    dimension = "Component Weight",
    param_value = label,
    is_baseline = (r$weight_case == "0.5_0.5"),
    dv_type = r$dv_type, domain = r$domain,
    effect = c("Total", "Direct", "Indirect"),
    beta   = c(r$tot_beta, r$dir_beta, r$ind_beta),
    ci_lo  = c(r$tot_ci_lo, r$dir_ci_lo, r$ind_ci_lo),
    ci_hi  = c(r$tot_ci_hi, r$dir_ci_hi, r$ind_ci_hi),
    sig    = c(r$tot_sig, r$dir_sig, r$ind_sig),
    stringsAsFactors = FALSE)
}))

# 3. Crop definition
cag_part <- do.call(rbind, lapply(seq_len(nrow(cag_sens)), function(i) {
  r <- cag_sens[i, ]
  data.frame(
    dimension = "Crop Definition",
    param_value = r$variant,
    is_baseline = grepl("baseline", r$variant),
    dv_type = r$dv_type, domain = r$domain,
    effect = c("Total", "Direct", "Indirect"),
    beta   = c(r$tot_beta, r$dir_beta, r$ind_beta),
    ci_lo  = c(r$tot_ci_lo, r$dir_ci_lo, r$ind_ci_lo),
    ci_hi  = c(r$tot_ci_hi, r$dir_ci_hi, r$ind_ci_hi),
    sig    = c(r$tot_sig, r$dir_sig, r$ind_sig),
    stringsAsFactors = FALSE)
}))

# Combine
all_robust <- rbind(win_part, wt_part, cag_part)

# Factor ordering
all_robust$effect <- factor(all_robust$effect, levels = c("Total", "Direct", "Indirect"))

all_robust$dv_label <- factor(
  ifelse(all_robust$dv_type == "RG", "Reported Say-do Gap",
  ifelse(all_robust$dv_type == "RB", "Reporting Bias (Green Illusion)",
         "Observed Market Behavior")),
  levels = c("Reported Say-do Gap", "Reporting Bias (Green Illusion)", "Observed Market Behavior"))

all_robust$dimension <- factor(all_robust$dimension,
  levels = c("Window Size", "Component Weight", "Crop Definition"))

# Param ordering within each dimension
win_order  <- paste0(seq(7, 21, 2), "\u00d7", seq(7, 21, 2))
wt_order   <- c("Mix 0.3 : Frag 0.7", "Mix 0.5 : Frag 0.5", "Mix 0.7 : Frag 0.3")
cag_order  <- c("CropAndGreen", "CropOnly (baseline)")
all_robust$param_value <- factor(all_robust$param_value,
  levels = c(win_order, wt_order, cag_order))

all_robust$beta_label <- paste0(sprintf("%.3f", all_robust$beta), " ", all_robust$sig)

# --- Plot: Grocery only ---
d_gro <- all_robust[all_robust$domain == "Grocery", ]

# Bold face for baseline rows
d_gro$face <- ifelse(d_gro$is_baseline, "bold", "plain")

p_robust_gro <- ggplot(d_gro, aes(x = beta, y = param_value, colour = effect, shape = effect)) +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey50") +
  geom_pointrange(aes(xmin = ci_lo, xmax = ci_hi),
                  size = .35, linewidth = .5,
                  position = position_dodge(width = .6)) +
  geom_text(aes(label = beta_label), vjust = -0.7, size = 2.2,
            show.legend = FALSE, position = position_dodge(width = .6)) +
  facet_grid(dimension ~ dv_label, scales = "free", space = "free_y") +
  scale_colour_manual(values = c(Total = "grey30", Direct = col_orange, Indirect = col_green)) +
  scale_shape_manual(values = c(Total = 16, Direct = 17, Indirect = 15)) +
  labs(x = expression("Standardised " * beta),
       y = NULL, colour = "Effect", shape = "Effect",
       title = "Desakota Index Robustness — Grocery Domain") +
  theme_minimal(base_size = 11) +
  theme(strip.text = element_text(face = "bold"),
        strip.text.y = element_text(angle = 0),
        strip.background.y = element_rect(fill = "grey92", colour = NA),
        legend.position = "bottom",
        panel.spacing.y = unit(.3, "lines"),
        axis.text.y = element_text(size = 8))

p_robust_gro
ggsave("FigS_robustness_grocery.png", p_robust_gro, width = 14, height = 12, dpi = 300)
```

```{r fig-robustness-combined, fig.width=16, fig.height=22, fig.cap="**Supplementary Fig. S** | Multiverse robustness of the Desakota Index."}

build_long <- function(sens_df, dim_label, param_col, baseline_val) {
  do.call(rbind, lapply(seq_len(nrow(sens_df)), function(i) {
    r <- sens_df[i, ]
    pv <- as.character(r[[param_col]])
    data.frame(
      dimension = dim_label, param = pv,
      is_baseline = (pv == as.character(baseline_val)),
      dv_type = r$dv_type, domain = r$domain,
      effect  = c("Total", "Direct", "Indirect"),
      beta    = c(r$tot_beta, r$dir_beta, r$ind_beta),
      sig     = c(r$tot_sig, r$dir_sig, r$ind_sig),
      stringsAsFactors = FALSE)
  }))
}

# Window: create label
win_sens$win_label <- paste0(win_sens$window, "\u00d7", win_sens$window)
long_win <- build_long(win_sens, "Window Size", "win_label",
                        paste0(9, "\u00d7", 9))

# Weight
wt_sens$wt_label <- ifelse(wt_sens$weight_case == "0.3_0.7", "Mix0.3:Frag0.7",
                    ifelse(wt_sens$weight_case == "0.5_0.5", "Mix0.5:Frag0.5",
                           "Mix0.7:Frag0.3"))
long_wt <- build_long(wt_sens, "Component Weight", "wt_label", "Mix0.5:Frag0.5")

# Crop definition
cag_sens$cag_label <- ifelse(grepl("baseline", cag_sens$variant), "CropOnly", "Crop+Green")
long_cag <- build_long(cag_sens, "Crop Definition", "cag_label", "CropOnly")

all_long <- rbind(long_win, long_wt, long_cag)
all_long$effect <- factor(all_long$effect, levels = c("Total", "Direct", "Indirect"))
all_long$dv_label <- factor(
  ifelse(all_long$dv_type == "Obs", "Observed Market Behavior",
  ifelse(all_long$dv_type == "RB", "Reporting Bias", "Reported Say-do Gap")),
  levels = c("Reported Say-do Gap", "Reporting Bias", "Observed Market Behavior"))

# ===================================================================
# PANEL A: p-value proxy histogram — all 3 effects, faceted
# ===================================================================

sig_to_p <- function(s) {
  ifelse(s == "***", 0.0005, ifelse(s == "**", 0.005,
  ifelse(s == "*", 0.03, 0.3)))
}
all_long$p_approx <- sig_to_p(all_long$sig)

p_A <- ggplot(all_long, aes(x = p_approx, fill = dv_label)) +
  geom_histogram(breaks = c(0, 0.001, 0.01, 0.05, 0.1, 0.5, 1),
                 colour = "white", linewidth = 0.3) +
  geom_vline(xintercept = 0.05, linetype = "dashed", colour = "red", linewidth = 0.6) +
  scale_fill_manual(values = c("Observed Market Behavior" = col_orange,
                                "Reporting Bias" = "#984ea3",
                                "Reported Say-do Gap" = "grey70")) +
  scale_x_continuous(breaks = c(0, 0.2, 0.5)) + 
  facet_wrap(~ effect, nrow = 1) +
  labs(x = "P value", y = "Frequency", fill = NULL,
       title = expression(bold("a. Distribution of P values across specifications (by effect type)"))) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom",
        strip.text = element_text(face = "bold"))


# ===================================================================
# PANEL B: Specification Curve (Total β sorted, by DV)
# ===================================================================

spec_data <- all_long[all_long$effect == "Total", ]
spec_data <- spec_data[order(spec_data$dv_label, spec_data$beta), ]
spec_data$rank <- ave(seq_len(nrow(spec_data)), spec_data$dv_label, FUN = seq_along)

p_B <- ggplot(spec_data, aes(x = rank, y = beta, colour = dv_label)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey50") +
  geom_point(aes(shape = ifelse(sig == "ns", "ns", "sig")), size = 2.2) +
  facet_wrap(~ dv_label, scales = "free", nrow = 1) +
  scale_colour_manual(values = c("Observed Market Behavior" = col_orange,
                                  "Reporting Bias" = "#984ea3",
                                  "Reported Say-do Gap" = "grey50")) +
  scale_shape_manual(values = c(sig = 16, ns = 1), guide = "none") +
  labs(x = "Specification (sorted by \u03b2)", y = expression("Total effect " * beta),
       colour = NULL,
       title = expression(bold("b. Specification curve: Total effect across all index variants"))) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none", strip.text = element_text(face = "bold"))


# ===================================================================
# PANELS C1 / C2 / C3: β heatmap for Total / Direct / Indirect
# ===================================================================

param_levels <- c(
  paste0(seq(7, 21, 2), "\u00d7", seq(7, 21, 2)),
  "Mix0.3:Frag0.7", "Mix0.5:Frag0.5", "Mix0.7:Frag0.3",
  "Crop+Green", "CropOnly"
)
col_levels <- c("Grocery\nRG", "Electronic\nRG",
                 "Grocery\nRB", "Electronic\nRB",
                 "Grocery\nObs", "Electronic\nObs")

make_heat <- function(eff_label, title_str, fill_limits) {
  hd <- all_long[all_long$effect == eff_label, ]
  hd$col_label  <- paste0(hd$domain, "\n", hd$dv_type)
  hd$param      <- factor(hd$param, levels = rev(param_levels))
  hd$col_label  <- factor(hd$col_label, levels = col_levels)
  hd$cell_label <- paste0(sprintf("%.2f", hd$beta), "\n", hd$sig)
  ggplot(hd, aes(x = col_label, y = param, fill = beta)) +
    geom_tile(colour = "white", linewidth = 0.5) +
    geom_text(aes(label = cell_label), size = 3.8, lineheight = 0.9) +
    geom_tile(data = hd[hd$is_baseline, ],
              colour = "red", fill = NA, linewidth = 0.8) +
    scale_fill_gradient2(low = col_green, mid = "white", high = col_orange,
                          midpoint = 0, limits = fill_limits,
                          name = expression(beta)) +
    labs(x = NULL, y = NULL, title = title_str) +
    theme_minimal(base_size = 12) +
    theme(axis.text.x = element_text(size = 12, face = "bold"),
          axis.text.y = element_text(size = 12),
          panel.grid = element_blank(),
          legend.position = "right",
          plot.title = element_text(face = "bold", size = 12))
}

p_C1 <- make_heat("Total",     expression(bold("c1. Total effect (β) across all specifications")),    c(-0.8, 0.7))
p_C2 <- make_heat("Direct",    expression(bold("c2. Direct effect (β) across all specifications")),   c(-0.8, 0.7))
p_C3 <- make_heat("Indirect", expression(bold("c3. Indirect effect (β) across all specifications")),  c(-0.5, 0.4))


# ===================================================================
# COMBINE: A / B / C1 / C2 / C3
# ===================================================================

p_A <- p_A + theme(plot.title = element_text(face = "bold", size = 12, hjust = 0))
p_B <- p_B + theme(plot.title = element_text(face = "bold", size = 12, hjust = 0))
p_C1 <- p_C1 + theme(plot.title = element_text(face = "bold", size = 12, hjust = 0))
p_C2 <- p_C2 + theme(plot.title = element_text(face = "bold", size = 12, hjust = 0))
p_C3 <- p_C3 + theme(plot.title = element_text(face = "bold", size = 12, hjust = 0))

p_combined <- p_A / p_B / p_C1 / p_C2 / p_C3 +
  plot_layout(heights = c(1.2, 1, 2, 2, 2))

p_combined
ggsave("FigS_robustness_multiverse.png", p_combined,
       width = 16, height = 22, dpi = 600)

write.csv(win_sens, "robustness_window_sensitivity.csv", row.names = FALSE)
write.csv(wt_sens,  "robustness_weight_sensitivity.csv", row.names = FALSE)
write.csv(cag_sens, "robustness_cropgreen_sensitivity.csv", row.names = FALSE)
```
